Preparing data from the Global Burden of Disease 2019 for METAHIT modelling

### 2021-11-08 metahit/paper_analyses.Rmd
Regenerate graphs

resplotnh %>%
  ggplot(aes(x=age, y=p50, group=area, col=area)) + 
  geom_ribbon(aes(ymin=plow, ymax=pupp), 
              fill="gray80", col="gray80") +
  geom_line() + 
  facet_grid(cols=vars(gender), rows=vars(disease), scales = "free_y", switch = "y") + 
  xlab("Age (years)") + 
  ylab("Annual case fatality probability") + 
  xlim(60,100) + 
  theme(strip.text.y.left = element_text(angle = 0),
        strip.text.y = element_text(size=6),
        axis.text = element_text(size=8),
        legend.text = element_text(size=6)) + 
    labs(col="")

grob <- ggplotGrob(gg)
# gtable::gtable_show_layout(grob)
idx <- which(grob$layout$name %in% c("panel-2-2","panel-8-2"))
for (i in idx) grob$grobs[[i]] <- grid::nullGrob()
grid::grid.draw(grob)

>>>>

gg <- resplotnh %>%
  ggplot(aes(x=age, y=p50, group=area, col=area)) + 
  geom_ribbon(aes(ymin=plow, ymax=pupp), 
              fill="gray80", col="gray80") +
  geom_line() + 
  facet_grid(cols=vars(gender), rows=vars(disease), scales = "free_y", switch = "y") + 
  xlab("Age (years)") + 
  ylab("Annual case fatality probability") + 
  xlim(60,100) + 
  theme(strip.text.y.left = element_text(angle = 0),
        strip.text.y = element_text(size=6),
        axis.text = element_text(size=8),
        legend.text = element_text(size=6)) + 
    labs(col="")

grob <- ggplotGrob(gg)
# gtable::gtable_show_layout(grob)
idx <- which(grob$layout$name %in% c("panel-2-2","panel-9-2"))
for (i in idx) grob$grobs[[i]] <- grid::nullGrob()
grid::grid.draw(grob)
